6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-09 paper.tex
Open Source

>>>>

\subsection{Additional Aims}

I will open source the project on GitHub, using a flexible and open license, as it could appeal to anyone with a general interest in infrastructure modelling and verification. Similar to a unit testing framework, the project would be pitched as a distributed modelling and testing framework for servers and other infrastructure. Open sourcing the project could have a number of benefits, such as:

\begin{itemize}
  \item Encouraging feedback and iterative improvement.
  \item The opportunity to build a community of contributors and plugins.
  \item Increased incentive to integrate with other open source DevOps tools such as Chef or Puppet.
  \item Better chances of adoption, as the tool would be free to use, modify and re-distribute.
\end{itemize}

If the project is open sourced, it could still be made available commercially in a hosted and supported form at a later date.
